

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}
We have introduced a sketch-based customized part extraction algorithm for 3D shape modeling. Our approach queries a database in real time and retrieves parts matching the user's sketch. In contrast to previous methods, our approach does not rely on a pre-segmented database. Instead, it generates customized parts on-the-fly to accurately match the sketch, thus significantly enriching the design space. Candidate parts are identified and segmented by a fast 2D-to-3D partial matching technique. Our algorithm enables several applications.

\textbf{Limitations.}  In our current implementation, we assume that the models in the database are manifold. Also, the contour descriptor we adopt is not scale-invariant.

\textbf{Future work.} We plan to develop more powerful scale-invariant contour descriptors. Since there have been several improvements to the angle descriptor~\cite{frompartialshapematchingcvpr}, we would like to incorporate these more powerful descriptors in our framework. In addition, it would be nice to incorporate cues from surrounding context to help disambiguate sketches.
\hl{Local symmetry/similarity matching could benefit from the context-based search.}
The view under which the sketch is drawn is important: some views are more discriminative than others. Helping users to draw optimal views and/or helping them interactively resolve ambiguous sketches, is an important research direction.
\hl{We plan to investigate the recognized definition of the partial matching problem in the future. }
\hl{It is also of interest to test our method in a more larger database. }
\hl{The fundamental premise of the sketch-based shape retrieval approaches is that the example database becomes larger by implicitly containing all possible segmented parts. We plan to investigate it in the future. }
\hl{The pose of the partial shape used for computing the boundary contours is important for our method.
If a suboptimal view is chosen, the method can return inappropriate candidate parts.
It would be interesting to explore the problem of best view selection in the future. } 